---
name:         Tuan Le Khac
jobtitle:     "Senior Data analyst | Risk management"
address:      "HCMC, SR Vietnam"
phone:        +84 32 891 8634
email:        "tuanlekhac@outlook.com"
linkedin:     tuanlekhac
date:         "`r format(Sys.time(), '%B %Y')`"
output:       function(...) {   source('tuan_cust_price_entries.R')
                          ;vitae:::set_entry_formats(price_entries)
                          ;vitae::cv_document(...   , template = "tuan_custome_pricetemplate.tex"
                                                    , citation_package = "biblatex")
                                        }

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(vitae)
library(lubridate)
library(glue)
library(rlang)
```
```{r loadData}
# Education
education <- readxl::read_xlsx("../data/education.xlsx",
                                1)  %>%
  as_tibble() %>%
  mutate(
    begin = as.Date(begin, format = "%m/%d/%y"),
    end = as.Date(end, format = "%m/%d/%y")
  )
# Education_detail
education_detail <- readxl::read_xlsx("../data/education_detail.xlsx",
                                1)  %>%
  as_tibble()
# Job titles
job.titles <- readxl::read_xlsx("../data/job-titles.xlsx",
                                1) %>%
  as_tibble() %>%
  mutate(
    begin = as.Date(begin, format = "%m/%d/%y"),
    end = as.Date(end, format = "%m/%d/%y")
  )
# Job descriptions
job.descriptions <-
  readxl::read_xlsx("../data/job-descriptions.xlsx",
                                1) %>%
  as_tibble()
# Skills
skills <-  readxl::read_xlsx("../data/skills.xlsx",
                            1) %>%
  as_tibble()
```

# About me

-   A dynamic and dedicated person, experienced in external audit & corporate finance, and currently working in the risk management field;

-   Long-term goal is to continuously accumulate knowledge of the market, operation, risk & strategy in banking & finance, strengthen data analytic skills to provide data-driven business solutions, and contribute to the organization.

# Education
```{r education, results = "asis"}
education %>% 
  # Format as detailed entries
  left_join(education_detail) %>% 
  arrange(descid) %>% 
  detailed_entries(
    what = degree,
    when = as.character(
      glue("{month(begin, label = TRUE, abbr = TRUE)} {year(begin)} - {month(end, label = TRUE, abbr = TRUE)} {year(end)}")),
    with = university,
    where = glue("{city}, {country}"),
    why = accomplishments)
```
# Work experience
```{r experience}
job.titles %>% 
  # Only 5 most recent jobs
  arrange(desc(begin)) %>% 
  filter(year(begin) >= 2010) %>%
  # Join job descriptions
  left_join(job.descriptions) %>% 
  # Arrange by descending begin date
  arrange(desc(begin), descId) %>% 
  # Format as detailed entries
  detailed_entries(
    what = position,
    when = as.character(
      glue("{month(begin, label = TRUE, abbr = TRUE)} {year(begin)} - 
           {if_else(!is.na(end), 
           paste(month(end, label = TRUE, abbr = TRUE), year(end)), 'Present')}")),
    with = glue("{department} - {employer}"),
    where = glue("{city}, {country}"),
    why = accomplishments)
```


# Skills
```{r}
skills_formatted <- skills %>% 
  arrange(order) %>% 
  mutate(skill = if_else(is.na(details)|details=="", glue("{skill}"), glue("{skill} ({details})"))) %>% 
  group_by(group, order) %>% 
  summarize(skills = glue_collapse(skill, sep = " $\\bullet$ ")) %>% 
  arrange(order)
```

```{r, results='asis', width = 40000}
for (group in skills_formatted$group) {
  cat(
    glue("\\textbf{<<tools::toTitleCase(group)>>}:", .open = "<<", .close = ">>"),
    filter(skills_formatted, group == !!group)$skills,
    "\n\n\n"
  )
}
```

# Languages
  Vietnamese, English, Chinese Mandarin (HSK5 equivalent).