\documentclass[11pt, letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    filecolor=magenta,      
    urlcolor=darkblue,
}
\usepackage{fancyhdr}
\usepackage{ragged2e}
\usepackage{xcolor}

\definecolor{darkblue}{RGB}{0,0,139}

\pagestyle{fancy}
\fancyhf{}
\rhead{ \textbf{\textcolor{darkblue}{Tuan Le Khac}}}
\rfoot{ \textit{\today}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\begin{document}

\thispagestyle{empty}

\noindent
\parbox[t]{0.45\textwidth}{\begin{flushleft}
Hiring Manager \\
Trusting Social
\end{flushleft}}
\hfill
\parbox[t]{0.45\textwidth}{\begin{flushright}
Tuan Le Khac \\
+84 32 891 8634 \\
\href{mailto:tuan.lekhac0905@gmail.com}{tuan.lekhac0905@gmail.com} \\
\href{https://linkedin.com/in/tuanlekhac}{linkedin.com/in/tuanlekhac}
\end{flushright}}


\noindent
\textbf{Subject: Application for Senior Data Analyst Position}

\vspace{0.2in}

Dear Hiring Manager,

\vspace{0.1in}
I am writing to express my keen interest in the Senior Data Analyst position at Trusting Social, as posted on \href{https://www.linkedin.com/jobs/view/4107882329}{Linked in}. With my strong foundation in financial analytics, extensive experience in risk management, and a proven track record of leveraging data to drive strategic decisions, I am confident I possess the skills and expertise necessary to excel in this role and significantly contribute to your team's success.

\vspace{0.1in}

In my previous role as Senior Data Analyst at \href{https://validus.vn/en/about-validus/}{Validus Vietnam} - a leading company in SEA for SME supply chain financing, I led end-to-end credit analytics initiatives, successfully optimizing credit policies and risk controls. This included developing and implementing a scorecard for MSMEs/Households lending products, managing data workflows, and streamlining cross-functional processes to enhance operational efficiency. These experiences have instilled in me a deep understanding of the importance of data integrity and accuracy, as well as the power of leveraging data to inform critical decisions.

\vspace{0.1in}

As detailed in my resume, I am proficient in a variety of data tools and technologies, including Excel, Power Query, Power BI, Google Sheets \& Apps Script, Looker Studio, Python, R, SQL, and PowerShell/Bash. My technical abilities, coupled with my strong analytical mindset, enable me to extract meaningful insights from complex datasets and effectively communicate them to stakeholders across various levels. I am particularly drawn to Trusting Social's commitment to [Mention something specific you admire about the company - e.g., innovative data solutions, impact in the financial inclusion space]. My passion for leveraging data to drive innovation aligns perfectly with this mission.

\vspace{0.1in}

I am eager to learn more about this opportunity and discuss how my skills and experiences can benefit Trusting Social. Thank you for your time and consideration. I look forward to hearing from you soon.

\vspace{0.2in}

Sincerely,
\vspace{0.1in}

\textbf{\textcolor{darkblue}{Tuan Le Khac}}

\end{document}